A survey of HTTP caching options on the open Web

### 2014-12-17 sanity/paper1.tex
Description of the fetching process fairly complete
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@904 43ef1190-90fd-4dd7-a769-d0121f02b80e

\section{Methodology}

@@

>>>>

\section{Implementation}

@@

We then developed a fairly elaborate paralell spider to get the
resources found on 3117 unique hosts in the previous steps using the
Perl frameworks RDF::Trine and libwww. The spider operated with a
timeout of 20 seconds and a maximum message size it would accept of 1
MB.

The paralell spider would then launch a process per host, but each
request to one host would be delayed by 10 seconds. For each host, the
spider would go through the list of URIs. Since the BTC2014 recorded
the \httph{Expires} (an RFC7234 caching header), \httph{Last-Modified}
and \httph{ETag} (RFC7232 conditional request) headers where they
existed, we first examined if any of the resources were still fresh,
but none were. Whereever the last two headers existed, we added the
corresponding \httph{If-Modified-Since} and \httph{If-None-Match}
headers for a conditional initial request.

For endpoints, we made the following SPARQL query:
\begin{verbatim}
SELECT REDUCED ?Concept WHERE {[] a ?Concept} LIMIT 2
\end{verbatim}
which should be quite light, yet likely yield results.

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\todo{footnote} to the Comprehensive Perl Archive
Network. We recorded whether the conditional request showed that the
BTC data were still fresh, and if it was, we retrieved the current
data, as we had not couple the headers to the body in our original
retrieval.

Based on the resulting headers, we first let libwww calculate the
freshness lifetime in seconds if it was possible, and recorded
that. Then, we also let it calculate a \emph{heuristic} freshness
time based on a suggestion in RFC7234, section~4.2.2, and record that.

If the initial response had RFC7232 headers, we make another
request to see if the server just included the headers but does not
actually support conditional requests. The heuristic we employed is
that if the headers remain the same, but the result was returned,
rather than just a response code \httph{304} (which indicates that the
previous result can be reused), then the server does most probably not
support it.

For endpoints, we examine the response message, to see if there are
any results to our query, and record that if there are.

For all others, we parsed the response, and recorded any errors if the
parser concluded the content were invalid. We noted that the Dublin Core
Metadata terms vocabulary has a number of predicates that may become
useful in determining heuristic freshness in the future, so we
recorded any statements containing the predicates \rdfterm{dct:date},
\rdfterm{dct:accrualPeriodicity}, \rdfterm{dct:created},
\rdfterm{dct:issued}, \rdfterm{dct:modified} or \rdfterm{dct:valid}.

For resource types other than ``vocabulary'', we look for SPARQL
endpoints in the response, using the predicates \rdfterm{sd:endpoint}
and \rdfterm{void:sparqlEndpoint}. We then do the same query as above
and record the relevant headers.

Finally, if the LOV SPARQL endpoint used a URI for the vocabulary that
was different from the namespace URI (after a normalization step),
another request would be made to record the selected HTTP headers from
that as well.
